---
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(DT)
```

<p id = "cat">Category</p>
<strong><p id = "title">By Player</p></strong>
<br><br>
<p id="section">Distribution Per Player</p>
<br>
<p id='desc'>How does the grade distribution per player look like? I think that's one of the first questions that came to my mind.</p>

```{r, message = FALSE, echo = FALSE, warning = FALSE, fig.width=14, fig.height=14}
setwd('~/github/dnvr_PlayerGrades/r')
source('data_wrangle.R', local = knitr::knit_global())

# grade distribution per player?
all_info %>% 
  count(grade, player) %>% 
  ggplot(aes(grade, n, fill = grade)) + 
  geom_histogram(stat = 'identity') + 
  facet_wrap(~player) +
  labs(x = 'Grades',
       y = 'Frequency') +
  theme(strip.text = element_text(size = rel(1.5)),
        axis.title = element_text(size = rel(1.5)),
        axis.text.y = element_text(size = rel(1.5)))
```

<p id='desc'>From this, you can kind of get an idea how each player fared. It's also interesting to see how the distribution shapes differ between players. It kind of gives you a window into how expectations are for them.<br><br> For example, how some players tended to receive a "default" grade. <i>(Donskoi was given a **D** grade much more frequent than his other grades.)</i></p>

<br><br>
<p id="section">GPA By Player</p>
<br>

<p id="desc">Distributions are great. But just like we did in the other page, it's easier to see the overall grade of a player when mapped to a GPA<br><br>This is one of my favorite graphics.</p>

```{r, message = FALSE, echo = FALSE, warning = FALSE, fig.width=14, fig.height=10}
setwd('~/github/dnvr_PlayerGrades/r')
source('data_wrangle.R', local = knitr::knit_global())

# GPA per player
all_info %>% 
  group_by(player) %>% 
  summarise(gpa = mean(gpa, na.rm = TRUE),
            games_played = n()) %>% 
  ggplot(aes(reorder(player, gpa), gpa, fill=games_played)) + 
  geom_bar(stat = 'identity') + 
  labs(x = 'Players',
       y = 'GPA') +
  theme(axis.text.x = element_text(angle = 90),
        axis.text = element_text(size = rel(1.5)),
        axis.title = element_text(size = rel(1.5)),
        legend.text = element_text(size = rel(1.5)),
        legend.title = element_text(size = rel(1.5)))
```

<p id='desc'></p>




<style>
@import url('https://fonts.googleapis.com/css2?family=Roboto:wght@500&display=swap');
@import url('https://fonts.googleapis.com/css2?family=Zilla+Slab:wght@300;500&display=swap');

#cat{
  margin: auto;
  text-align: center;
  font-size: 20px;
  font-family: 'Roboto', sans-serif;
}

#title{
  margin: auto;
  text-align: center;
  font-size: 40px;
  font-family: 'Roboto', sans-serif;
}

#desc{
  font-size: 20px;
  font-family: 'Roboto', sans-serif;
}

#section{
  margin: auto;
  text-align: center;
  font-family: 'Zilla Slab', serif;
  font-size: 30px;
  color: #2553CC;
}

</style>