---
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(DT)
```

<p id = "cat">Category</p>
<strong><p id = "title">By Player</p></strong>
<br><br>
<p id="section">Distribution Per Player</p>
<br>
<p id='desc'>How does the grade distribution per player look like? I think that's one of the first questions that came to my mind.</p>

```{r, message = FALSE, echo = FALSE, warning = FALSE, fig.width=14, fig.height=14}
setwd('~/github/dnvr_PlayerGrades/r')
source('data_wrangle.R', local = knitr::knit_global())

# grade distribution per player?
all_info %>% 
  count(grade, player) %>% 
  ggplot(aes(grade, n, fill = grade)) + 
  geom_histogram(stat = 'identity') + 
  facet_wrap(~player)
```












<style>
@import url('https://fonts.googleapis.com/css2?family=Roboto:wght@500&display=swap');
@import url('https://fonts.googleapis.com/css2?family=Zilla+Slab:wght@300;500&display=swap');

#cat{
  margin: auto;
  text-align: center;
  font-size: 20px;
  font-family: 'Roboto', sans-serif;
}

#title{
  margin: auto;
  text-align: center;
  font-size: 40px;
  font-family: 'Roboto', sans-serif;
}

#desc{
  font-size: 20px;
  font-family: 'Roboto', sans-serif;
}

#section{
  margin: auto;
  text-align: center;
  font-family: 'Zilla Slab', serif;
  font-size: 30px;
  color: #2553CC;
}

</style>