---
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(DT)
```

<p id = "cat">Category</p>
<strong><p id = "title">Data Overview</p></strong>
<br><br>
<p id="portada">La Portada</p>
<br><br>
<p id="desc">Have you ever read through power rankings, mock-drafts, or projected standings, and wondered: "does anyone actually ever look back to see how they did?"<br><br>Maybe I'm the only one who thinks about that. <br><br>In any case, I don't know if anyone would be interested in seeing if there was anything captivating in DNVR's Avalanche player grades, but I thought it would be cool!
<br><br><i>Especially since the nature of player grades is so interesting</i>. Tangent to grades in a school, player grades tend to be fairly -  to completely - arbitrary: at the discretion of the author. They are non-standardized, meaning that an <strong>"A"</strong> for Nathan MacKinnon probably isn't the same as an  <strong>"A"</strong> for Matt Nieto. One could say they are a reflection of what how a player performs against what is expected.<br><br>So what could analyzing the grades tell us? Probably what you would expect! A little about how each player's season went, as well as what the authors tend to think about them.</p>

<br><br>
<p id="portada">A Little Note About the Data:</p>
<br><br>

<p id="desc">Since a lot of this was messy, manual data input, there are prone to exists typos and errors: I did my best to validate myself, but it was a lot of freaking inputting.<br><br>Also, there are about 5 games that I, or DNVR, omitted from the data. 3 were missing from DNVR's grades section, and for the last 2 games of each playoff series, DNVR decided to do <i>series grades</i> instead of that specific game. And to maintain consistency, I did not include them.</p>

<br><br>
<p id="portada">The Data</p>
<br><br>

```{r, message = FALSE, echo = FALSE, warning = FALSE}
setwd('~/github/dnvr_PlayerGrades/r')
source('data_wrangle.R', local = knitr::knit_global())

# make data table
datatable(all_info, class = 'hover', options = list(pageLength = 10),
          colnames = c("game", 
                       "date",
                       "gametype",
                       "author",
                       "plus_minus",
                       "num_goals",
                       "grade",
                       "player_id",
                       "player",
                       "position",
                       "gpa Id"))


```




<style>
@import url('https://fonts.googleapis.com/css2?family=Roboto:wght@500&display=swap');
@import url('https://fonts.googleapis.com/css2?family=Zilla+Slab:wght@300;500&display=swap');

#cat{
  margin: auto;
  text-align: center;
  font-size: 20px;
  font-family: 'Roboto', sans-serif;
}

#title{
  margin: auto;
  text-align: center;
  font-size: 40px;
  font-family: 'Roboto', sans-serif;
}

#desc{
  font-size: 20px;
  font-family: 'Roboto', sans-serif;
}

#portada{
  margin: auto;
  text-align: center;
  font-family: 'Zilla Slab', serif;
  font-size: 30px;
  color: #2553CC;
}

</style>
