---
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(DT)
```

<p id = "cat">Category</p>
<strong><p id = "title">Data Overview</p></strong>
<br><br>
<p id="section">Overall Grade Distribution</p>
<br>
<p id="desc">We'll start with the overall grade distribution.<br>You can see right-off-the-bat that whole grades were used much more frequently than partial grades.<br>You can also see that the grades <strong>A</strong>, <strong>B</strong>, and <strong>C</strong> were used the most, around 2.5 times per game.<br>Note that <strong>INC</strong> happened when a player played very little.</p>
<br><br>
```{r, message = FALSE, echo = FALSE, warning = FALSE, fig.width=14, fig.height=7}
setwd('~/github/dnvr_PlayerGrades/r')
source('data_wrangle.R', local = knitr::knit_global())

# overall grade distribution?
all_info %>% 
  count(grade) %>% 
  mutate(per_game = round(n/length(game), 1)) %>% 
  ggplot(aes(grade, n, fill = grade)) + 
  geom_histogram(stat = 'identity') +
  labs(y = 'Frequency',
       x = 'Grade',
       subtitle = 'usage per game marked in graph') +
  theme(legend.position = "none",
        axis.title.x = element_text(size = rel(2.5)),
        axis.title.y = element_text(size = rel(2.5)),
        axis.text.x = element_text(size = rel(2.5)),
        axis.text.y = element_text(size = rel(2.5)),
        plot.subtitle = element_text(size = rel(2))) +
  geom_text(aes(label = per_game), size = 10, nudge_y = 5)
```
<br><br><br><br>
<p id="section">Articles per Author</p>
<br>
<p id="desc">Looks like this is mostly Evan's assignment.<br>Also note that these dates are when the article was posted, not when the game was played.</p>
```{r, message = FALSE, echo = FALSE, warning = FALSE, fig.width=18, fig.height=7}
setwd('~/github/dnvr_PlayerGrades/r')
source('data_wrangle.R', local = knitr::knit_global())

# author count
base_game %>% 
  count(author, date) %>% 
  count(author, date) %>% 
  ggplot(aes(x = date, y = n, fill = author)) +
  geom_bar(stat = 'identity', size = 3.5) +
  theme(axis.title.x = element_text(size = rel(2.5)),
        axis.title.y = element_text(size = rel(2.5)),
        axis.text.x = element_text(size = rel(2.5)),
        axis.text.y = element_text(size = rel(2.5)),
        legend.text = element_text(size = rel(2)),
        legend.title = element_text(size = rel(2))) +
  labs(x = 'Date Graded', y = '')
```
<br><br>
```{r, message = FALSE, echo = FALSE, warning = FALSE, fig.width=18, fig.height=7}
setwd('~/github/dnvr_PlayerGrades/r')
source('data_wrangle.R', local = knitr::knit_global())

# author count
base_game %>% 
  count(author) %>%
  ggplot(aes(author, n, fill = author)) +
  geom_bar(stat = 'identity') +
  labs(x = 'Author',
       y = 'Games Graded') +
  theme(axis.title.x = element_text(size = rel(2.5)),
        axis.title.y = element_text(size = rel(2.5)),
        axis.text.x = element_text(size = rel(2.5)),
        axis.text.y = element_text(size = rel(2.5)),
        legend.position = 'none') +
  geom_text(aes(label = n), size = 10, nudge_y = 5)

```








<style>
@import url('https://fonts.googleapis.com/css2?family=Roboto:wght@500&display=swap');
@import url('https://fonts.googleapis.com/css2?family=Zilla+Slab:wght@300;500&display=swap');

#cat{
  margin: auto;
  text-align: center;
  font-size: 20px;
  font-family: 'Roboto', sans-serif;
}

#title{
  margin: auto;
  text-align: center;
  font-size: 40px;
  font-family: 'Roboto', sans-serif;
}

#desc{
  font-size: 20px;
  font-family: 'Roboto', sans-serif;
}

#section{
  margin: auto;
  text-align: center;
  font-family: 'Zilla Slab', serif;
  font-size: 30px;
  color: #2553CC;
}

</style>
