---
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(DT)
```

<p id = "cat">Category</p>
<strong><p id = "title">Introduction</p></strong>
<br><br>
<p id="portada">La Portada</p>
<br><br>
<p id="desc">This is nothing more, or less, than me having some fun. Look, we know that if a player plays well, they get a good grade. Part of the fun of this is to see if there is anything else that could possibly influence the grade, but also just to prove what we already know in colorful graphs!</p>

<br><br>
<p id="portada">A Little Note About the Data:</p>
<br><br>

<p id="desc">Since a lot of this was messy, manual data input, there are prone to exists typos and errors: I did my best to validate myself, but it was a lot of freaking inputting.<br><br>Also, there are about 5 games that I, or DNVR, omitted from the data. 3 were missing from DNVR's grades section, and for the last 2 games of each playoff series, DNVR decided to do <i>series grades</i> instead of that specific game. And to maintain consistency, I did not include them.</p>

<br><br>
<p id="portada">The Data</p>
<br><br>

```{r, message = FALSE, echo = FALSE, warning = FALSE}
setwd('~/github/dnvr_PlayerGrades/r')
source('data_wrangle.R', local = knitr::knit_global())

# make data table
datatable(all_info, class = 'hover', options = list(pageLength = 10),
          colnames = c("game", 
                       "date",
                       "gametype",
                       "author",
                       "plus_minus",
                       "num_goals",
                       "grade",
                       "player_id",
                       "player",
                       "position",
                       "gpa Id"))


```




<style>
@import url('https://fonts.googleapis.com/css2?family=Roboto:wght@500&display=swap');
@import url('https://fonts.googleapis.com/css2?family=Zilla+Slab:wght@300;500&display=swap');

#cat{
  margin: auto;
  text-align: center;
  font-size: 20px;
  font-family: 'Roboto', sans-serif;
}

#title{
  margin: auto;
  text-align: center;
  font-size: 40px;
  font-family: 'Roboto', sans-serif;
}

#desc{
  font-size: 20px;
  font-family: 'Roboto', sans-serif;
}

#portada{
  margin: auto;
  text-align: center;
  font-family: 'Zilla Slab', serif;
  font-size: 30px;
  color: #2553CC;
}

</style>
