---
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(DT)
```

<p id = "cat">Category</p>
<strong><p id = "title">Performance</p></strong>
<br><br>
<p id="section">Record & Time</p>
<br>
<p id="desc">One of the first questions I jotted down when looking through the data was <i>how did the grades look in respect to time</i>?<br><br>I decided to break "time" down into individual months. It seemed like the appropriate granularity, having about 10 games per month.<br><br>The following is the first graph shown in <strong> Data Overview</strong>, broken up into monthly buckets *(their win-loss record in the title)*.</p>

```{r, message = FALSE, echo = FALSE, warning = FALSE, fig.width=14, fig.height=14}
setwd('~/github/dnvr_PlayerGrades/r')
source('data_wrangle.R', local = knitr::knit_global())

# grades per month
all_info %>% 
  mutate(month = month(date, label = TRUE)) %>% 
  count(grade, month) %>% 
  inner_join(record) %>% 
  mutate(record = factor(record, levels = c('Oct 8-4',
                                          'Nov 8-6',
                                          'Dec 7-6',
                                          'Jan 5-4',
                                          'Feb 11-3',
                                          'Mar 3-3',
                                          'Aug 6-5',
                                          'Sep 2-0'))) %>% 
  ggplot(aes(grade, n, fill = grade)) + geom_histogram(stat = 'identity') + facet_wrap(~record, nrow = 4) +
  theme(legend.position = "none",
        axis.title.x = element_text(size = rel(2.5)),
        axis.title.y = element_text(size = rel(2.5)),
        axis.text.x = element_text(size = rel(2.5)),
        axis.text.y = element_text(size = rel(2.5)),
        plot.subtitle = element_text(size = rel(2)),
        strip.text = element_text(size=25)) +
  labs(x = 'Grade',
       y = 'Frequency')

```

<br>
<p id="desc">Here we have **time**, and **record**. Time itself probably is a difficult variable to analyze, since record probably influences the grades more. However, in the pictures you can see that *partial grades* seem to be more used as time went on. Was that a thing? The *partial grades* section may have more.<br><br>**Record** seems like it has some sort of a sway. In months where their record was better, the distribution seems to hug the left a little more.<br><br>Record is nice, but isn't the only proxy for performance.</p>

<br><br>
<p id="section">Performance by Scoring Differential</p>
<br>

<p id="desc">How about **scoring differential?** It adds a more information about a game, than just whether it was a win, or a loss - while inferring outcome.</p>

```{r, message = FALSE, echo = FALSE, warning = FALSE, fig.width=10, fig.height=10}
setwd('~/github/dnvr_PlayerGrades/r')
source('data_wrangle.R', local = knitr::knit_global())

# grade distribution per +/-?
all_info %>% 
  count(grade, plus_minus) %>% 
  ggplot(aes(grade, n, fill = grade)) + 
  geom_histogram(stat = 'identity') + 
  facet_wrap(~plus_minus, nrow = 3) +
  theme(legend.position = "none",
        axis.title.x = element_text(size = rel(1.5)),
        axis.title.y = element_text(size = rel(1.5)),
        axis.text.x = element_text(size = rel(1), angle = 90),
        axis.text.y = element_text(size = rel(1.5)),
        plot.subtitle = element_text(size = rel(2)),
        strip.text = element_text(size=25)) +
  labs(x = 'Grades',
       y = 'Frequency')


```

<p id="desc">As expected, the grades shift towards the left *(higher)* when the Avs' scoring differential is higher.<br><br>However, it's still a little hard to see. To make it easier, I mapped the grades to a common **GPA** system *(0-4)*.</p>



```{r, message = FALSE, echo = FALSE, warning = FALSE, fig.width=10, fig.height=7}
setwd('~/github/dnvr_PlayerGrades/r')
source('data_wrangle.R', local = knitr::knit_global())

# gpa per +/-
all_info %>% 
  group_by(plus_minus) %>% 
  summarise(gpa = mean(gpa, na.rm = TRUE),
            count = n()) %>% 
  ggplot(aes(plus_minus,gpa, fill = count)) + geom_bar(stat = 'identity') +
  theme(axis.title.x = element_text(size = rel(1.5)),
        axis.title.y = element_text(size = rel(1.5)),
        axis.text.x = element_text(size = rel(1), angle = 90),
        axis.text.y = element_text(size = rel(1.5)),
        plot.subtitle = element_text(size = rel(2)),
        strip.text = element_text(size=25)) +
  labs(x = 'Differential',
       y = 'GPA')

```

<p id='desc'>Also as expected, it appears that as scoring differential improves, so does the GPA.</p>






<style>
@import url('https://fonts.googleapis.com/css2?family=Roboto:wght@500&display=swap');
@import url('https://fonts.googleapis.com/css2?family=Zilla+Slab:wght@300;500&display=swap');

#cat{
  margin: auto;
  text-align: center;
  font-size: 20px;
  font-family: 'Roboto', sans-serif;
}

#title{
  margin: auto;
  text-align: center;
  font-size: 40px;
  font-family: 'Roboto', sans-serif;
}

#desc{
  font-size: 20px;
  font-family: 'Roboto', sans-serif;
}

#section{
  margin: auto;
  text-align: center;
  font-family: 'Zilla Slab', serif;
  font-size: 30px;
  color: #2553CC;
}

</style>
